Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-20 code/scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
included eval in main
added comments

\documentclass[letterpaper]{article}

\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{color}

\begin{document}

 \section{Evaluation}

To evaluate our progress toward building a cognitive system capabile of reasoning about these regions, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{How well do anchor points capture context-dependent spatial regions?}
\item{When provided with an example definition of a CDSR, how well does our approach identify the CDSR in the new situation?}
\item{Is the integration of geometric and semantic knowledge necessary?}
\item{Does similarity correlate with performance?}
\end{itemize}

@@

\subsection{Materials}
We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. To determine how people consider CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons representing a list of region types for seach room, users were also shown a polygon drawn by another and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons.

We consider a \textit{problem instance} to be a room and a sought CDSR type (e.g., "front"). For each room containing a CDSR of the sought type, we generate an \textit{inferred region} our analogical approach. To assess the quality of the transfer, we use the following measures:

@@

As a baseline, we will compare our results against the manually encoded CDSRS for the problem instance and the entire room. The precision and recall for considering the entire room provides a baseline from which to assess each of the questions. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and a ceiling for the inferred region performance.

@@

If we are just going to report means, we should standard deviations as well.

@@

@@

\subsection{Discussion}
Our results

\end{document}

>>>>

\section{Evaluation}\label{sec:evaluation}

To evaluate our progress toward building a cognitive system capable of reasoning about these CDSRs, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{How well do anchor points capture context-dependent spatial regions?}
\item{When provided with a base representation containing a labelled CDSR, how well does our approach identify the CDSR in a given target?}
\item{Is the integration of geometric and semantic knowledge necessary?}
\item{Does similarity correlate with performance?}
\end{itemize}

@@

\subsection{Materials}
We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. To determine how people define CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons for particular region types for each room. Users were also shown a polygon drawn by another user and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons.

\from{Nick}{What is the base CDSR in a problem instance?}

We consider a \textit{problem instance} to be a room and a sought CDSR type (e.g., ``front''). For each room for which we have a human-labelled target CDSR of the sought type, we generate an \textit{inferred region} using our analogical approach. To assess the quality of the transfer, we use the following measures:

@@

As a baseline, we will compare our results against the manually encoded CDSRs for the problem instance and the entire room. The precision and recall for considering the entire room provides a baseline from which to assess each of the questions. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and a ceiling for the inferred region performance.

\from{Nick}{What are manually encoded CDSRs? Are these the ones you do and use for the base case?}

@@

\from{Nick}{Would this be just a single region type or averaging across all applicable ones?}

If we are just going to report means, we should standard deviations as well. %yup!

@@

% this would be lovely!

@@

\subsection{Discussion}

Our results
